### 2014-05-05 Docs/lo_density/lo_density.tex
add note about limit_conductivity

These are working notes for the low density parameters in \maestro.
In low density regions, we modify the behavior of the algorithm.  Here
is a summary of some parameters, and a brief description of what they
do.
\begin{itemize}
\item {\tt base\_cutoff\_density}, $\rho_{\rm base}$, (real):\\ \\
Essentially controls the lowest density allowed in the simulation and modifies the behavior
of several modules.
\item {\tt base\_cutoff\_density\_coord(:)} (integer array):\\ \\
For each level in the radial base state array, this is the coordinate of the first cell
where $\rho_0 < \rho_{\rm base}$.  Slightly more complicated for multilevel problems.
\item {\tt anelastic\_cutoff}, $\rho_{\rm anelastic}$, (real):\\ \\
If $\rho_0 < \rho_{\rm anelastic}$, we modify the computation of $\beta_0$ in the
divergence constraint.
\item {\tt anelastic\_cutoff\_coord(:)} (integer array):\\ \\
Anelastic cutoff analogy of {\tt base\_cutoff\_density\_coord(:)}.
\item {\tt burning\_cutoff\_density}, $\rho_{\rm burning}$,  (real):\\ \\
If $\rho < \rho_{\rm burning}$, don't call the burner in this cell.
\item {\tt burning\_cutoff\_density\_coord(:)} (integer array):\\ \\
Burning cutoff analogy of {\tt base\_cutoff\_density\_coord(:)}.
\item {\tt buoyancy\_cutoff\_factor} (real):\\ \\
When computing velocity forcing, set the buoyance term ($\rho-\rho_0$) to 0 if 
$\rho < $ {\tt buoyancy\_cutoff\_factor} * {\tt base\_cutoff\_density}.
\item {\tt do\_eos\_h\_above\_cutoff} (logical):\\ \\
If {\rm true}, at the end of the advection step, for each cell where 
$\rho < \rho_{\rm base}$, recompute $h = h(\rho,p_0,X)$.
\end{itemize}

@@

Note that for single-level planar or any spherical problem, saying $r\ge$ {\tt anelastic\_cutoff\_coord} is analogous to saying $\rho_0(r)\le$ {\tt anelastic\_cutoff}.  Also, saying $r<$ {\tt anelastic\_cutoff\_coord} is analogous to saying $\rho_0(r)>$ {\tt anelastic\_cutoff}.  Ditto for {\tt base\_cutoff\_density} and {\tt base\_cutoff\_density\_coord}.

@@

The {\tt anelastic\_cutoff} is the density below which we modify the constraint.

@@

\item in {\tt make\_S}, we set {\tt delta\_gamma1\_term} and {\tt delta\_gamma1} 
  to zero for $r \ge {\tt anelastic\_cutoff\_coord}$.

@@

The {\tt base\_cutoff\_density} is the lowest density that we model.

@@

\item In {\tt update\_scal}, if $\rho \le {\tt base\_cutoff\_density}$
   and {\tt do\_eos\_h\_above\_cutoff}, we call the EOS to compute $h$.

@@

\item In {\tt probin}, {\tt burning\_cutoff\_density} is set to 
  {\tt base\_cutoff\_density}.  There is no option to set 
  {\tt burning\_cutoff\_density} using the inputs file.

@@

The {\tt buoyancy\_cutoff\_factor} is used to zero out the forcing terms
to the velocity equation at low densities.

@@

>>>>

These are working notes for the low density parameters in \maestro.
In low density regions, we modify the behavior of the algorithm.  Here
is a summary of some parameters, and a brief description of what they
do.
\begin{itemize}
\item \runparam{base\_cutoff\_density}, $\rho_{\rm base}$, (real):\\ \\
Essentially controls the lowest density allowed in the simulation and modifies the behavior
of several modules.
\item {\tt base\_cutoff\_density\_coord(:)} (integer array):\\ \\
For each level in the radial base state array, this is the coordinate of the first cell
where $\rho_0 < \rho_{\rm base}$.  Slightly more complicated for multilevel problems.

\item \runparam{anelastic\_cutoff}, $\rho_{\rm anelastic}$, (real):\\ \\
If $\rho_0 < \rho_{\rm anelastic}$, we modify the computation of $\beta_0$ in the
divergence constraint.

\item {\tt anelastic\_cutoff\_coord(:)} (integer array):\\ \\
Anelastic cutoff analogy of {\tt base\_cutoff\_density\_coord(:)}.

\item \runparam{burning\_cutoff\_density}, $\rho_{\rm burning}$,  (real):\\ \\
If $\rho < \rho_{\rm burning}$, don't call the burner in this cell.

\item {\tt burning\_cutoff\_density\_coord(:)} (integer array):\\ \\
Burning cutoff analogy of {\tt base\_cutoff\_density\_coord(:)}.

\item \runparam{buoyancy\_cutoff\_factor} (real):\\ \\
When computing velocity forcing, set the buoyance term ($\rho-\rho_0$) to 0 if 
$\rho < $ {\tt buoyancy\_cutoff\_factor} * {\tt base\_cutoff\_density}.

\item \runparam{do\_eos\_h\_above\_cutoff} (logical):\\ \\
If {\rm true}, at the end of the advection step, for each cell where 
$\rho < \rho_{\rm base}$, recompute $h = h(\rho,p_0,X)$.
\end{itemize}

@@

Note that for single-level planar or any spherical problem, saying
$r\ge$ {\tt anelastic\_cutoff\_coord} is analogous to saying
$\rho_0(r)\le$ \runparam{anelastic\_cutoff}.  Also, saying $r<$ {\tt
anelastic\_cutoff\_coord} is analogous to saying $\rho_0(r)>$ {\tt
anelastic\_cutoff}.  Ditto for \runparam{base\_cutoff\_density} and {\tt
base\_cutoff\_density\_coord}.

@@

The \runparam{anelastic\_cutoff} is the density below which we modify the constraint.

@@

\item in {\tt make\_S}, we set {\tt delta\_gamma1\_term} and {\tt delta\_gamma1} 
  to zero for $r \ge {\tt anelastic\_cutoff\_coord}$.  This is only relevant
  if you are running with \runparam{use\_delta\_gamma1\_term} {\tt = T}.

@@

The \runparam{base\_cutoff\_density} is the lowest density that we model.

@@

\item In {\tt update\_scal}, if $\rho \le {\tt base\_cutoff\_density}$
   and \runparam{do\_eos\_h\_above\_cutoff}, we call the EOS to compute $h$.

@@

\item In {\tt probin}, \runparam{burning\_cutoff\_density} is set to 
  \runparam{base\_cutoff\_density}.  There is no option to set 
  {\tt burning\_cutoff\_density} using the inputs file.

@@

The \runparam{buoyancy\_cutoff\_factor} is used to zero out the forcing terms
to the velocity equation at low densities.

@@

\item In {\tt make\_explicit\_thermal}, if \runparam{limit\_conductivity} {\tt = T}, then for 
$\rho < \mathtt{buoyancy\_cutoff\_factor}$ \\ $* \mathtt{base\_cutoff\_density}$, we
zero out the thermal coefficients, effectively turning off thermal
diffusion there.

### 2014-05-05 Docs/visualization/visualization.tex
update the getting started with some new info

By default, plotfiles store double precision data, but if {\tt
  single\_prec\_plotfiles = .true.} is set, then the data is converted
to single precision before outputting---this is done to reduce file
sizes.

@@

{\tt rhoh}   & $(\rho h)$ & {\tt use\_tfromp = F} or ({\tt use\_tfromp = T} and {\tt plot\_h\_with\_use\_tfromp = T}) \\           

@@

{\tt X(*)}   & $(\rho X_k)/\rho$ & {\tt plot\_spec} \\

@@

{\tt tracer} & tracers           & {\tt plot\_trac} \\

@@

{\tt w0\_x}  & $w_0 \er \cdot \ex$ & {\tt plot\_base} \\ 

@@

{\tt radial\_velocity}  & $\Ubt \cdot \er + w_0$ & {\tt spherical == 1} \\

@@

{\tt soundspeed}        & $c(\rho,p_0,X_k)$ & {\tt plot\_cs} \\

@@

{\tt sponge} or {\tt sponge\_fdamp} & $1/(1 + \Delta t \kappa f_\mathrm{damp})$ by default; $f_\mathrm{damp}$ if {\tt plot\_sponge\_fdamp = T} & -- \\

@@

{\tt gpi\_x}           & $\nabla \pi \cdot \ex$ & {\tt plot\_gpi} \\

@@

{\tt omegadot(*)}      & $\dot{\omega}_k$ & {\tt plot\_omegadot} \\

@@

{\tt enucdot}          & $(\rho \Hnuc)/\rho$ & {\tt plot\_Hnuc} \\

@@

{\tt Hext}             & $(\rho \Hext)/\rho$ & {\tt plot\_Hext} \\

@@

{\tt eta\_rho}         & $\etarho$ & {\tt plot\_eta} \\

@@

{\tt thermal}          & $\nabla \cdot \kappa \nabla T$ & {\tt use\_thermal\_diffusion} \\

@@

{\tt ad\_excess}       & $\nabla - \nabla_\mathrm{ad}$ & {\tt plot\_ad\_excess} \\

@@

{\tt particle\_count}  & number of particles in a cell & {\tt use\_particles} \\

@@

{\tt processor\_number} & processor number containing the cell's data & {\tt plot\_processors} \\

@@

{\tt pi\_divu}         & $\pi \nabla \cdot \tilde{\Ub}$ (a measure of energy conservation) & {\tt plot\_pidivu} \\

@@

%-----------------------------------------------------------------------------
% yt
%-----------------------------------------------------------------------------
\section{Visualizing with \yt}

>>>>

By default, plotfiles store double precision data, but if
\runparam{single\_prec\_plotfiles} {\tt = T} is set, then the data is
converted to single precision before outputting---this is done to
reduce file sizes.

@@

{\tt rhoh}   & $(\rho h)$ & {\tt use\_tfromp = F} or ({\tt use\_tfromp = T} and \runparam{plot\_h\_with\_use\_tfromp} {\tt = T}) \\           

@@

{\tt X(*)}   & $(\rho X_k)/\rho$ & \runparam{plot\_spec} \\

@@

{\tt tracer} & tracers           & \runparam{plot\_trac} \\

@@

{\tt w0\_x}  & $w_0 \er \cdot \ex$ & \runparam{plot\_base} \\ 

@@

{\tt radial\_velocity}  & $\Ubt \cdot \er + w_0$ & \runparam{spherical} {\tt == 1} \\

@@

{\tt soundspeed}        & $c(\rho,p_0,X_k)$ & \runparam{plot\_cs} \\

@@

{\tt sponge} or {\tt sponge\_fdamp} & $1/(1 + \Delta t \kappa f_\mathrm{damp})$ by default; $f_\mathrm{damp}$ if \runparam{plot\_sponge\_fdamp = T} & -- \\

@@

{\tt gpi\_x}           & $\nabla \pi \cdot \ex$ & \runparam{plot\_gpi} \\

@@

{\tt omegadot(*)}      & $\dot{\omega}_k$ & \runparam{plot\_omegadot} \\

@@

{\tt enucdot}          & $(\rho \Hnuc)/\rho$ & \runparam{plot\_Hnuc} \\

@@

{\tt Hext}             & $(\rho \Hext)/\rho$ & \runparam{plot\_Hext} \\

@@

{\tt eta\_rho}         & $\etarho$ & \runparam{plot\_eta} \\

@@

{\tt thermal}          & $\nabla \cdot \kappa \nabla T$ & \runparam{use\_thermal\_diffusion} \\

@@

{\tt ad\_excess}       & $\nabla - \nabla_\mathrm{ad}$ & \runparam{plot\_ad\_excess} \\

@@

{\tt particle\_count}  & number of particles in a cell & \runparam{use\_particles} \\

@@

{\tt processor\_number} & processor number containing the cell's data & \runparam{plot\_processors} \\

@@

{\tt pi\_divu}         & $\pi \nabla \cdot \tilde{\Ub}$ (a measure of energy conservation) & \runparam{plot\_pidivu} \\

@@

%-----------------------------------------------------------------------------
% yt
%-----------------------------------------------------------------------------
\section{\label{sec:vis:yt} Visualizing with \yt}
